Instructions for developing new pages for the MarineOmics webpage

### 2023-12-13 DRAFT_DNA_methylation.Rmd
adding expectations to intro
Update DRAFT_DNA_methylation.Rmd

- Sequence quality assessment
- Read alignment
- Methylation quantification
- File conversions
- Potential downstream applications. Although this tutorial will not provide code for downstream applications, it will link to other open-access resources and examples.

@@

An example of what raw data might look like from a marine invertebrate is shown. *Note that DNA methylation patters are diverse across taxa with most marine invertebrates demonstrating a mosiac pattern and global methylation at CpG loci is approximately 15%.*

Following trimming one would expect to see something similar to this. This particular data set was trimmed with the following parameters:

@@

The software used as part of this tutorial is **Bismark Bisulfite Mapper**. As with any software it is best to be famililar with the [User Manual](https://rawgit.com/FelixKrueger/Bismark/master/Docs/Bismark_User_Guide.html). Thus content below will provided with the assumption that the reader has read the manual and is meant to serve as guidance based on experience working with marine invertebrates.

>>>>

- Sequence quality assessment
- Read alignment
- Methylation quantification
- File conversions
- Potential downstream applications. Although this tutorial will not provide code for downstream applications such as differential methylation analysis, it will link to other open-access resources and examples.

@@

An example of what raw data might look like from a marine invertebrate is shown. *Note that DNA methylation patters are diverse across taxa with most invertebrates demonstrating a mosiac pattern and global methylation at CpG loci is approximately 15%.*

Following trimming one would expect to see FastQC per base sequencing content similar to the plot shown below. This particular data set was trimmed with the following parameters:

@@

The software used as part of this tutorial is **Bismark Bisulfite Mapper** (@http://dx.doi.org/10.1093/bioinformatics/btr167). As with any software it is best to be famililar with the [User Manual](https://rawgit.com/FelixKrueger/Bismark/master/Docs/Bismark_User_Guide.html). The content below will provided with the assumption that the reader has read the manual and is meant to serve as guidance based on experience working with marine invertebrates.
